Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
modif table timings

\begin{figure}[!htbp]
  \begin{center}
    \begin{tikzpicture}[scale=0.7]
%      \begin{axis}[
%          ybar stacked,
%          ymode = log,
%	  	  bar width=20pt,
%	  	  nodes near coords,
%	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
%          enlargelimits=0.15,
%          ylabel={\#Time (in ms)},
%          symbolic x coords={Octa-R8, Octa-R16, Snow-R1, Snow-R2,
%	      xxx-R1, xxx-R2},
%          xtick=data,
%          point meta=rawy,
%          x tick label style={rotate=45,anchor=east},
%        ]
%        \addplot+[ybar] plot coordinates {(Octa-R8,11.7) (Octa-R16,11.682000)
%          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,1)};
%        \addplot+[ybar] plot coordinates {(Octa-R8,7.401000) (Octa-R16,7.666000)
%          (Snow-R1,1) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,1)};
%        \addplot+[ybar] plot coordinates {(Octa-R8,27.226000) (Octa-R16,25.328000)
%          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
%        \addplot+[ybar] plot coordinates {(Octa-R8,184.161000) (Octa-R16,169.501000)
%          (Snow-R1,1) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
%        \addplot+[ybar] plot coordinates {(Octa-R8, 1) (Octa-R16,1189.127000)
%          (Snow-R1,1) (Snow-R2,1) (xxx-R1,1) (xxx-R2,1)};
%        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
%      \end{axis}

      \begin{axis}[
          ybar stacked,
          ymode = log,
          ymax = 6000,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar, color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000)
          (Snow-R10,9.831000) (Snow-R20,9.653000)  (Dragon-R8,136.300000) (Dragon-R20,145.450000)};
        %l4
        \addplot+[ybar, color=black, fill=clquatre] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000)
          (Snow-R10,6.085000) (Snow-R20,9.445000)  (Dragon-R8,3.389000) (Dragon-R20,20.228000)};
        %l3
        \addplot+[ybar, color=black, fill=cltrois] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
          (Snow-R10,10.629000) (Snow-R20,11.542000) (Dragon-R8,20.397000) (Dragon-R20,26.710000)};
        %l2
        \addplot+[ybar, color=black, fill=cldeux] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000)
          (Snow-R10,13.777000) (Snow-R20,37.700000) (Dragon-R8,29.967000) (Dragon-R20,92.435000)};
        %l1
        \addplot+[ybar, color=black, fill=clun] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000)
          (Snow-R10,39.627000) (Snow-R20,217.954000) (Dragon-R8,59.840000) (Dragon-R20,506.549000)};
        %l0
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000)
          (Snow-R10,236.194000) (Snow-R20,1655.680000) (Dragon-R8,322.674000) (Dragon-R20,3763.422000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
	  \end{tikzpicture}
%
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymax = 6000,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          %ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar,color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000)
          (Snow-R10,9.383000) (Snow-R20,9.767000)  (Dragon-R8,127.347000) (Dragon-R20,127.166000)};
        %Hierarchical measurement
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000)
          (Snow-R10,96.747000) (Snow-R20,364.547000)  (Dragon-R8,147.662000) (Dragon-R20,787.459000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}

     \end{tikzpicture}
     \end{center}
  \caption{Timings obtained while visualizing an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm.
  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (dark blue).
  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii ($8$, $10$, $16$ and $20$)}
  \label{fig:timings}
\end{figure}

>>>>

\begin{figure}[!htbp]
  \begin{center}
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymode = log,
          ymax = 6000,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar, color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000)
          (Snow-R10,9.831000) (Snow-R20,9.653000)  (Dragon-R8,136.300000) (Dragon-R20,145.450000)};
        %l4
        \addplot+[ybar, color=black, fill=clquatre] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000)
          (Snow-R10,6.085000) (Snow-R20,9.445000)  (Dragon-R8,3.389000) (Dragon-R20,20.228000)};
        %l3
        \addplot+[ybar, color=black, fill=cltrois] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
          (Snow-R10,10.629000) (Snow-R20,11.542000) (Dragon-R8,20.397000) (Dragon-R20,26.710000)};
        %l2
        \addplot+[ybar, color=black, fill=cldeux] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000)
          (Snow-R10,13.777000) (Snow-R20,37.700000) (Dragon-R8,29.967000) (Dragon-R20,92.435000)};
        %l1
        \addplot+[ybar, color=black, fill=clun] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000)
          (Snow-R10,39.627000) (Snow-R20,217.954000) (Dragon-R8,59.840000) (Dragon-R20,506.549000)};
        %l0
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000)
          (Snow-R10,236.194000) (Snow-R20,1655.680000) (Dragon-R8,322.674000) (Dragon-R20,3763.422000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
	  \end{tikzpicture}
%
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymax = 6000,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          %ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar,color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000)
          (Snow-R10,9.383000) (Snow-R20,9.767000)  (Dragon-R8,127.347000) (Dragon-R20,127.166000)};
        %Hierarchical measurement
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000)
          (Snow-R10,96.747000) (Snow-R20,364.547000)  (Dragon-R8,147.662000) (Dragon-R20,787.459000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
     \end{tikzpicture}
     \end{center}
  %
  \caption{Timings in milliseconds obtained while visualizing an adaptive
  triangulation on three objects -- OctaFlower (digital domain of $130^3$ ), Snow
  Microstructures ($233^3$) and XYZ-Dragon ($510^3$) --  by computing the
  curvature with a regular grid (\emph{left}) and with hierarchical
  algorithm (\emph{right}), with two different radii for each object.
  %
  In \emph{orange color}: time required to extract the triangulation.
  %
  In \emph{blue color}: time required to compute the curvature tensor at
  different levels: from $l_4$ (light blue) to $l_0$ (dark blue).
  %
  }
  %
  \label{fig:timings}
\end{figure}
